Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-07 pnas/Towards.tex
no message

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

@@

\begin{abstract}
Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs. To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.  Appendix~\ref{sec:numeric_details} provides additional details on the experiments.

@@

\section*{Acknowledgment}
The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, and Fred Sigworth for supplying us with the dataset of the BPTI molecule. The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
\revised{Amit: to verify.} NB is partially supported by NSF award DMS-1719558.
\TODO{Correct bib}

@@

this is necessary to  determine the volume.

>>>>

% Please add here a significance statement to explain the relevance of your work
\significancestatement{A common states that small molecules cannot be reconstructed using cryo-EM. In this paper, we show that this argument is flaw and show }

@@

\begin{abstract}

Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

The technique we advocate allows recovery of a signal hidden in noisy micrographs without detecting the location  of the signals embedded in these micrographs. To illustrate the underlying principles of the method, we present several numerical examples for the toy model~\eqref{eq:model} and a simple proof of concept for simulated cryo-EM data.  Appendix~\ref{sec:numeric_details} provides additional details on the experiments. 
\revised{The code to generate all figures is publicly available in TKTK.}

@@

\section*{Acknowledgment}
The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, Fred Sigworth for supplying us with the dataset of the BPTI molecule,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
 The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
\revised{Amit: to verify.} NB is partially supported by NSF award DMS-1719558.
\TODO{Correct bib}

@@
